Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying

### 2023-02-21 Outputs/Paper/paper.qmd
Update paper.qmd

@fig-1 shows the number of Google hits for all 'bullying' searches in the top ten states with the highest Asian populations. According to Bacher-Hicks, there is a positive correlation between search intensity and frequency of victimization (Bacher-Hicks, 8). While unusually high peaks occur during March 2017 and 2018 with the frequency reaching 400, and the lowest clicks during summer months with numbers consistently below 200, the overall trend from 2016 to the start of the pandemic shows an overall decline. In 2020, when the pandemic began well known to the public, there continues to be a decline in overall search intensity. On average the 2020 frequency was lower than in previous years. This was the same time period when most schools were shut down and classes were offered online which could lead to the conclusion that bullying decreased when students were not attending classes in person. There is a slight rise in the summer of 2020 that is compared to the 2016 data and a reverse of the declining trends seen over the years, however, the following summer this number is reduced to the lowest number seen over the years. This blimp at the start of the pandemic could be a result of students being in lock down with more online time. Overall, the trend in search frequency and therefore, victimization, has been relatively stable with a slight decline up to the start of the pandemic and then we see further declines as a result of online learning, school closures and isolation during COVID-19. This graph shows there was no increase in bullying of Asian students by their peers during the pandemic in the top ten states with high Asian populations.

>>>>

@fig-1 shows the number of Google hits for all 'bullying' searches in the top ten states with the highest Asian populations. According to Bacher-Hicks, there is a positive correlation between search intensity and frequency of victimization (Bacher-Hicks, 8). While unusually high peaks occur during March 2017 and 2018 with the frequency reaching 400, and the lowest clicks during summer months with numbers consistently below 200, the overall trend from 2016 to the start of the pandemic shows an overall decline. In 2020, when the pandemic began well known to the public, there continues to be a decline in overall search intensity. On average the 2020 frequency was lower than in previous years. This was the same time period when most schools were shut down and classes were offered online which could lead to the conclusion that bullying decreased when students were not attending classes in person. There is a slight rise in the summer of 2020 that is compared to the 2016 data and a reverse of the declining trends seen over the years, however, the following summer this number is reduced to the lowest number seen over the years. This blimp at the start of the pandemic could be a result of students being in lock down with more online time.

@fig-2 shows the frequency of the amount of searches for "Cyberbullying". The naked eye test will tell you that the amount of cyberbullying searches have slightly decreased every year from 2016. The lowest points of the graph occur from 2020 onwards. The summer months are always the lowest througout the five years with a slight decrease every year. The peak of the data happens in March of 2016 climbing up to 500 compared to March 2020 when it's 250. This is a drast difference between pre and post pandemic.

Overall, the trend in search frequency and therefore, victimization, has been relatively stable with a slight decline up to the start of the pandemic and then we see further declines as a result of online learning, school closures and isolation during COVID-19. This graph shows there was no increase in bullying of Asian students by their peers during the pandemic in the top ten states with high Asian populations.
